Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-26 authors.tex

\textbf{Vahid Rostami}$^{28\S}$,

@@

\textbf{Guillaume Viejo}$^{33\S}$,

@@

\textbf{Julien Vitay}$^{34\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Anya Vostinar}$^{35\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Roman Yurchak}$^{36\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Tiziano Zito}$^{37\dagger}$\\

>>>>

\textbf{Vahid Rostami}$^{28\S}$\href{http://orcid.org/0000-0002-3851-0220}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Federico Vaggi}$^{33\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Guillaume Viejo}$^{34\S}$,

@@

\textbf{Julien Vitay}$^{35\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Anya Vostinar}$^{36\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},

@@

\textbf{Roman Yurchak}$^{37\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
\textbf{Tiziano Zito}$^{38\dagger}$\\
